Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
CL bit

% !TeX spellcheck = en_GB
\documentclass{article}

@@

	% Import table content
	\input{tables/cl_table_1}
\end{wraptable}
%
% Overview
We aim to highlight our sparse representation's ability to retain prior knowledge within a continual learning (CL) setting (as in \cref{sec:sequential}). Notably, CL methods require tuning making direct comparisons difficult. We consider the setup with single-head (SH) setting that is typically hard and more competitive.
%
% Benchmarks/architectures
We consider the CL benchmarks: Sequential-MNIST (S-MNIST), Sequential-FashionMNIST (S-FMNIST), and Permuted-MNIST (P-MNIST). We follow the setups described in \cite{rudner2022continual, pan2020continual}, using a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST (full details in \cref{app:cl-exp}).

% Methods
We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR. We also introduce an ablation study where we replace $\bar{\MB}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior (giving an L2 regularizer).
Following \cite{rudner2022continual}, we use 200 inducing points per tasks. Additionally,  we consider only 40 inducing points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.

>>>>

% !TeX spellcheck = en_US
\documentclass{article}

@@

	% Import table content
	\input{tables/cl_table_1}
\end{wraptable}
%
% Overview

We aim to highlight our sparse representation's ability to retain prior knowledge for continual learning (CL) (as in \cref{sec:sequential}). We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
%
% Benchmarks/architectures
 Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST). We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency. Please refer to \cref{app:cl-exp} for full details.

% Methods
We compare our method against two categories of methods: {\em (i)}~weight-regularization methods: EWC, SI, and VCL (which additionally incorporates coresets), and {\em(ii)}~function-based regularization methods: DER, FROMP, S-FSVI, SFR. We also introduce an ablation study where we replace $\bar{\MB_t}^{-1}$ with an identity matrix $\MI_M$, equivalent to assuming a GP with i.i.d.\ prior with a unit variance (giving an L2 regularizer).
Following \cite{rudner2022continual}, we use 200 points per tasks. Additionally,  we consider only 40 points for S-MNIST, to investigate if our method was still capable of capture more information due to its sparse formulation.
